Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-17 manuscript.Rmd
tiny fix to minimal effects test paragraph
Added wordcount (4969)

keywords          : "Equivalence Testing, NHST, power, TOST, falsification."
wordcount         : "X"

@@

Alternatively, the researcher could decide that even if the true ratio in the population is not exactly 0.015, the null hypothesis should consist of a range of values around the difference in proportions of 0.015 that can be considered trivially small. The researcher could for example test if the difference is smaller than -0.005, and larger than 0.035. This test against two bounds, with $H_0$ being a range rather than one value (see Figure 1B), is known as a *minimal effects test* [@Murphy2014].

>>>>

keywords          : "Equivalence Testing, NHST, power, TOST, falsification."
wordcount         : "4969"

@@

Alternatively, the researcher could decide that even if the true ratio in the population is not exactly 0.015, the null hypothesis should consist of a range of values around the difference in proportions of 0.015 that can be considered trivially small. The researcher could for example test if the difference is smaller than -0.005, or larger than 0.035. This test against two bounds, with $H_0$ being a range rather than one value (see Figure 1B), is known as a *minimal effects test* [@Murphy2014].
